### 2020-01-27 draft.tex
Added covariate tables to appendix and other minor wording adjustments

\date{January 14, 2020}

@@

A few modeling decisions should be explicitly mentioned. First, these models do not include any additional controls. The RIN price system is complex and nonlinear \citep{Serra2011}, and our intent is to determine more generally the presence or absence of any dynamic feedback between RINs and firm prices, not to unravel the complex and interwoven channels through which that feedback occurs. Relevant covariates would almost certainly vary between RINs, further complicating estimation and sacrificing interpretability. Whatever limitations the exclusion of these covariates might impose on the interpretation of our modelling results, they are much less of a concern for the event study models, which (as will be seen) correspond quite tightly to the VAR results. We do, however, re-run the D5 models with the Russel 3000 index and WTI oil price index as separate added covariates for robustness. Second, we deviate from authors like \cite{Knittel2017} in estimating VAR models for each RIN separately rather than a single per-gallon-of-gasoline RIN obligation, constructed as a pre-specified linear combination of RIN prices. Since the shocks in this study are to expectations regarding the final RIN obligations (including the weights of various RIN types), constructing a ``total obligation" is not straightforward; the expected end-of-year RIN obligation should vary with EPA announcements and that variation should affect both firm and RIN prices. Keeping things at the individual RIN level allows us to avoid imposing additional assumptions regarding how firms generate expectations of final obligations.

@@

The results from bivariate time series analysis suggest that the impacts of RIN price movements are not homogeneous across firms. In fact, most small- and medium-size firms' values are not impacted by the lagged values of RIN prices. By contrast, large firms show negative reactions to RIN price movements after a few lags. This is especially evident in results from D5 bivariate modeling in Table \ref{d5timeseries}, where Chevron (CVX), British Petroleum (BP), Shell (RDS.A), and Total (TOT) all have negative fourth lag terms significant at the 5\% level. Exxon Mobil (XOM), the only remaining large market cap firm in the data, is also negatively associated with D5 RINs, but only at the 10\% significance level. The fact that only large firms exhibit significant negative responses is not an artifact of the optimal lag selection procedure; reproductions of Tables \ref{d6timeseries}, \ref{d5timeseries}, and \ref{d4timeseries} for models that were forced to six lags are available in the appendix and have no major qualitative differences. Re-running the D5 models with either the Russel 3000 index or WTI oil price added as a covariate (forcing six lags across the board) similarly results in significant negative price responses at lags 4-5 for large firms and no others.

@@

>>>>

\date{January 27, 2020}

@@

A few modeling decisions should be explicitly mentioned. First, these models do not include any additional controls. The RIN price system is complex and nonlinear \citep{Serra2011}, and our intent is to determine more generally the presence or absence of any dynamic feedback between RINs and firm prices, not to unravel the complex and interwoven channels through which that feedback occurs. Relevant covariates would almost certainly vary between RINs, further complicating estimation and sacrificing interpretability. Whatever limitations the exclusion of these covariates might impose on the interpretation of our modelling results, they are much less of a concern for the event study models, which (as will be seen) correspond quite tightly to the VAR results. We do, however, re-run the D5 models with the Russel 3000 index and WTI oil price index as separate added covariates for robustness. Second, we deviate from authors like \cite{Knittel2017} in estimating VAR models for each RIN separately rather than a single per-gallon-of-gasoline RIN obligation, constructed as a pre-specified linear combination of RIN prices. Since the shocks in this study are to expectations regarding the final RIN obligations (including the weights of the  RIN types), constructing a ``total obligation" is not straightforward; the expected makeup of the end-of-year RIN obligation should vary with EPA announcements and that variation should affect both firm and RIN prices. Keeping things at the individual RIN level allows us to avoid imposing additional assumptions regarding how firms generate expectations of final obligations.

@@

The results from bivariate time series analysis suggest that the impacts of RIN price movements are not homogeneous across firms. In fact, most small- and medium-size firms' values are not impacted by the lagged values of RIN prices. By contrast, large firms show negative reactions to RIN price movements after a few lags. This is especially evident in results from D5 bivariate modeling in Table \ref{d5timeseries}, where Chevron (CVX), British Petroleum (BP), Shell (RDS.A), and Total (TOT) all have negative fourth lag terms significant at the 5\% level. Exxon Mobil (XOM), the only remaining large market cap firm in the data, is also negatively associated with D5 RINs, but only at the 10\% significance level. The fact that only large firms exhibit significant negative responses is not an artifact of the optimal lag selection procedure; reproductions of Tables \ref{d6timeseries}, \ref{d5timeseries}, and \ref{d4timeseries} for models that were forced to six lags are available in the appendix and have no major qualitative differences. Re-running the D5 models with either the Russel 3000 index or WTI oil price added as a covariate (forcing six lags across the board) similarly results in significant negative price responses at lags 4-5 for large firms and no others; these results are also available in the appendix.

@@

\subsection{Bivariate Time Series D5 Models with Covariates}

\begin{table}[!htbp] \centering 
	\caption{Bivariate Time Series Model with D5 RINs and RUS3000 Covariate} 
	\label{d5timeseries6lags} 
	\resizebox{\textwidth}{!}{
		\begin{tabular}{@{\extracolsep{0pt}} lcccccccccccc} 
			\hline 
			\hline \\[-1.8ex] 
			\input{tables/D5VARRUS3000_edited.tex}
			\hline 
		\end{tabular} 
	}
	\begin{flushleft}
		\scriptsize{Note: Column headers are stock tickers corresponding to firms as in Table \ref{bins}. Each column reports results from a VAR model as described in Equation \ref{var} with the inclusion of the Russel 3000 index as a covariate. Lag order is forced to six. Significance at alpha levels of 0.1, 0.05, and 0.01 are reported with *, **, and ***, respectively.}\\
	\end{flushleft}
\end{table}

\begin{table}[!htbp] \centering 
	\caption{Bivariate Time Series Model with D5 RINs and WTI Covariate} 
	\label{d5timeseries6lags} 
	\resizebox{\textwidth}{!}{
		\begin{tabular}{@{\extracolsep{0pt}} lcccccccccccc} 
			\hline 
			\hline \\[-1.8ex] 
			\input{tables/D5VARWTI_edited.tex}
			\hline 
		\end{tabular} 
	}
	\begin{flushleft}
		\scriptsize{Note: Column headers are stock tickers corresponding to firms as in Table \ref{bins}. Each column reports results from a VAR model as described in Equation \ref{var} with the inclusion of the WTI oil price index as a covariate. Lag order is forced to six. Significance at alpha levels of 0.1, 0.05, and 0.01 are reported with *, **, and ***, respectively.}\\
	\end{flushleft}
\end{table}
